Seasonal Variation in Marriage License Applications

### 2024-09-26 paper/paper.qmd
title edit

# install.packages("tidyverse")
# install.packages("ggplot2")
# install.packages("dplyr")
# install.packages("readr")
# install.packages("janitor")
# install.packages("opendatatoronto")
# install.packages("knitr")
# install.packages("here")
# install.packages("kableExtra")
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readr)
library(janitor)
library(opendatatoronto)
library(knitr)
library(here)
library(kableExtra)

@@

@@

## Civil Center Comparison

>>>>

# install.packages("tidyverse")
# install.packages("ggplot2")
# install.packages("dplyr")
# install.packages("readr")
# install.packages("janitor")
# install.packages("opendatatoronto")
# install.packages("knitr")
# install.packages("here")
# install.packages("kableExtra")
# install.packages("lubridate")
library(lubridate)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readr)
library(janitor)
library(opendatatoronto)
library(knitr)
library(here)
library(kableExtra)

@@

```{r}
#| label: february-table
#| fig-cap: "Table 1: Total Marriage Licenses Issued in February for Each Year"
#| echo: false
#| warning: false
#| message: false

# Summarize February Data: Filter for February and calculate the total number of licenses
february_data <- data %>%
  filter(month == "02") %>%  # Filter for February
  group_by(year) %>%  # Group by year
  summarise(february_licenses = sum(marriage_licenses))  # Summarize total licenses in February

# Create a table of February marriage licenses for each year
knitr::kable(
  february_data,
  caption = "Table: Total Marriage Licenses Issued in February for Each Year",
  col.names = c("Year", "February Licenses"),
  format = "simple"
)

```{r}
#| label: february-plot
#| fig-cap: "Figure 1: Total Marriage Licenses Issued in February (2011-2023)"
#| echo: false
#| warning: false
#| message: false

# Plot Total February Licenses Over Time
ggplot(february_data, aes(x = year, y = february_licenses)) +
  geom_line(color = "steelblue", size = 1) +
  geom_point(color = "red", size = 3) +  # Optional: Add points for each year
  labs(title = "Total Marriage Licenses Issued in February (2011-2023)",
       x = "Year",
       y = "Number of Licenses") +
  theme_minimal()

```{r}
#| label: monthly-totals-table
#| fig-cap: "Table 2: Total Monthly Marriage Licenses by Year"
#| echo: false
#| warning: false
#| message: false

# Monthly Summary for All Months: Group data by year and month to calculate total licenses
monthly_totals <- data %>%
  group_by(year, month) %>%
  summarise(total_licenses = sum(marriage_licenses))

# Create a table of monthly totals by year
knitr::kable(
  tidyr::spread(monthly_totals, year, total_licenses),  # Reshape data to display years side by side
  caption = "Table: Total Monthly Marriage Licenses by Year",
  col.names = c("Month", unique(monthly_totals$year)),  # Dynamically add years as column names
  format = "simple"
)

@@

```{r}
#| label: december-table
#| fig-cap: "Table 3: Total Marriage Licenses Issued in December for Each Year"
#| echo: false
#| warning: false
#| message: false

# Summarize December Data: Filter for December and calculate the total number of licenses
december_data <- data %>%
  filter(month == "12") %>%  # Filter for December
  group_by(year) %>%  # Group by year
  summarise(december_licenses = sum(marriage_licenses))  # Summarize total licenses in December

# Create a table of December marriage licenses for each year
knitr::kable(
  december_data,
  caption = "Table: Total Marriage Licenses Issued in December for Each Year",
  col.names = c("Year", "December Licenses"),
  format = "simple"
)

```
```{r}
#| label: december-plot
#| fig-cap: "Figure 2: Total Marriage Licenses Issued in December (2011-2023)"
#| echo: false
#| warning: false
#| message: false

# Plot Total December Licenses Over Time
ggplot(december_data, aes(x = year, y = december_licenses)) +
  geom_line(color = "green", size = 1) +
  geom_point(color = "red", size = 3) +  # Optional: Add points for each year
  labs(title = "Total Marriage Licenses Issued in December (2011-2023)",
       x = "Year",
       y = "Number of Licenses") +
  theme_minimal()

```
## Civil Center Comparison
